---
title: "`r params$title %||% 'Metabolomics Data Quality Report'`"
output:
  html_document:
    theme:
      version: 5
      bootswatch: cosmo
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
params:
  title:
    value: "Metabolomics Data Quality Report"
  notes:
    value: ""
  plots:
    value: !r character(0)
  p:
    value: !r NULL
  d:
    value: !r NULL
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(dev = "png")
library(htmltools)
library(dplyr)
library(MetaboRx)
```
# Raw Data
<!-- ### Metabolite columns removed before correction -->
```{r}
#MetaboRx:::report_text_withheld_columns(params$p, params$d)
```

### Raw Data Summary and Structural Checks
```{r}
MetaboRx:::ui_basic_info(params$d$cleaned)
#MetaboRx:::report_text_data_inspection()
```

### Filter Missing Values in Raw Data
```{r}
MetaboRx:::ui_filter_info(params$d$filtered)
```
### Blank Threshold Filtering
```{r}
MetaboRx:::ui_blank_threshold_info(params$d$filtered$blank_threshold_result, 
                                       params$d$cleaned$blank_df,
                                       params$d$filtered$blank_threshold,
                                       params$d$filtered$remove_blank_threshold_cols,
                                       params$d$filtered$removed_blank_threshold_cols)
#MetaboRx:::report_text_mv_filter()
```

# Imputation, Signal Drift Correction, and Transformation.

### Missing Value Imputation
```{r}
MetaboRx:::report_text_imputation(params$p, params$d)
```

### Correction Description
```{r}
MetaboRx:::report_text_correction(params$p, params$d)
#MetaboRx:::report_text_correction_descriptions()
```
##### How to choose a correction method
```{r}
MetaboRx:::ui_how_to_correct(params$d$filtered$df)
```

### Post-correction Filtering
#### QC RSD Filtering

```{r}
#MetaboRx:::report_text_rsd_cal()
MetaboRx:::ui_postcor_filter_info(params$d$filtered_corrected,
                                      params$p$remove_imputed, 
                                      params$p$rsd_cutoff, 
                                      MetaboRx:::.qc_rsd_filter_enabled(params$p, params$p$rsd_cutoff),
                                      params$p$remove_qc_average_pct_filter)
```
```{r}
MetaboRx:::ui_rsd_stats(compare_to = "filtered_cor_data", params$p, params$d)
MetaboRx:::report_text_rsd_table()
```

### Candidate Extreme Values

```{r, echo=FALSE, fig.width=7.5, fig.height=5.5}
hp <- params$plots[["Hotelling PCA"]]
if (!is.null(hp)) {
  print(hp)
} else {
  htmltools::tags$span(style = "font-weight:bold;", "Hotelling PCA plot was not available.")
}
```
```{r}
MetaboRx:::ui_outliers_table(params$d$hotelling_res) 
#MetaboRx:::report_text_ev_detection()
```

### Transformation
```{r}
MetaboRx:::report_text_transformation(params$p, params$d)
#MetaboRx:::report_text_transform_methods()
```

#### RSD Post-transformation Comparison
```{r}
MetaboRx:::ui_rsd_stats(compare_to = "transformed_cor_data", params$p, params$d)
#MetaboRx:::report_text_rsd_tc_table()
```

###  Metabolite Correlations
```{r}
#MetaboRx:::report_text_correlations()
if (!is.null(params$d$all_corr)) {
  MetaboRx:::ui_corr_range_info(params$d$all_corr, params$p$corr_threshold)
} else {
  htmltools::tags$span(style = "font-weight:bold;", "Metabolite correlations were not computed.")
}
```
# Visualization

### Visualize the Correction with Metabolite Scatter Plots
```{r, echo=FALSE, fig.show='hold', out.width='49%', fig.width=5, fig.height=5}
print(params$plots[["Metabolite Scatter 1"]])
print(params$plots[["Metabolite Scatter 2"]])
```
```{r}
MetaboRx:::report_text_scatter_intro(params$p, params$d)
MetaboRx:::report_text_met_scatter()
```

### RSD Comparison Plots
To judge the quality of the cleaned data, we can visualize the change in variation with the relative standard deviation (RSD) comparison plots. RSD is sometimes called coefficient of variation (CV) and is computed as RSD = (standard deviation / mean) * 100%. High RSD indicates that the values for that metabolite are more spread out around the mean, which may be an expected result in the experimental samples. For QC samples, RSD should decrease after correction.
```{r}
MetaboRx:::report_text_rsd_intro(params$p, params$d)
```
```{r, echo=FALSE, fig.width=7.5, fig.height=4.5}
print(params$plots[["RSD Comparison"]])
```
```{r}
MetaboRx:::report_text_rsd_plots()
```

### PCA Comparison Plots
To evaluate the quality of the cleaned data principal component analysis (PCA) score plots help visualize metabolomics data, identify sample groups, and determine which metabolites contribute the most variation. 

```{r, echo=FALSE, fig.width=8.333, fig.height=4.417}
print(params$plots[["PCA Comparison"]])
```

```{r, echo=FALSE, fig.width=8.75, fig.height=4.417}
print(params$plots[["PCA Loading"]])
```
```{r}
MetaboRx:::report_text_pca_plots()
```
